Batch Bayesian Optimization via Multi-objective Acquisition Ensemble for Automated Analog Circuit Design

### 2018-02-09 paper/background.tex
minor revisions

The objective function $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} can be
approximated by Gaussian process (GP) model~\cite{GPML}. The GP model is the
most commonly used model for Bayesian optimization. The advantage of GP is that
it provides a well-calibrated uncertainty of prediction. GP is characterized by
a mean function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In
this work, we use squared-exponential ARD kernel, and a constant mean function
$m(\bm{x}) = \mu_0$ for all our experiments, by default, we assume the
objective function evaluations are noisy and let GP to infer the noise level
$\sigma_n$, the introduction of the $\sigma_n$ level also helps to improve the
numerical stability.

>>>>

The objective function $\mathrm{FOM}(\bm{x})$ in \eqref{eq:Formulation} can be
approximated by Gaussian process (GP) model~\cite{GPML}. The GP model is the
most commonly used model for Bayesian optimization. The advantage of GP is that
it provides a well-calibrated uncertainty of prediction. GP is characterized by
a mean function $m(\bm{x})$ and a covariance function $k(\bm{x}, \bm{x'})$. In
this work, we use squared-exponential ARD kernel, and a constant mean function
$m(\bm{x}) = \mu_0$ for all our experiments. By default, we assume the
objective function evaluations are noisy and let GP to infer the noise level
$\sigma_n$. The introduction of the $\sigma_n$ level also helps to improve the
numerical stability.

### 2018-02-09 paper/experiments.tex
minor revisions

The proposed MACE algorithm was tested using eight benchmark functions and two
real-world circuits. For the two test circuits, we used HSPICE 2012.06 to as
the simulator to get circuit performances.

@@

We also ran the MACE algorithm in sequential mode and compared with the EI and LCB
acquisition functions, the sequential EI and LCB based Bayesian optimization
are implemented by setting the batch size $B = 1$ for EI-LP and BLCB
respectively.

The mean performances of the tested algorithms on the benchmark functions are
plotted in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
optimization results are listed in Table~\ref{tab:result_analytical}. As can be
seen in Figure~\ref{fig:CovPlotBenchmark} and
Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
algorithm is competitive with the LCB and EI acquisition functions. The MACE-1
algorithm gave better performances than EI-1 and LCB-1 in the Eggholder,
Branin, Hartmann6, Ackley10, and Rosenbrock10 functions. Also, the parallel
MACE (MACE-4) gave the best performances among all the tested algorithms for
six out of the eight benchmark functions, and has shown dramatic speedup
compared to the sequential MACE (MACE-1).

@@

We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier, the Figure of Merit $FOM$ is constructed as:
$$
\mathit{FOM} = -1.2 \times \mathit{gain} - 10 \times \mathit{UGF} - 1.6 \times \mathit{PM}
$$

@@

The mean convergence plot for the sequential and batch runs are given in
Figure~\ref{fig:resDAC2014}, the mean and standard deviation of the final
optimized FOM values are listed in Table~\ref{tab:result_opamp}. As can be
seen, on average, the batch MACE algorithm had the fastest convergence rate
compared with the sequential MACE algorithm and other parallel algorithms. It
should also be noted that the final optimized FOM values given by MACE-4 have
very small deviation (0.105) compared with other algorithms.

@@

For this power amplifier, we aim to maximize the power added efficiency (PAE) and the output power (Pout), the Figure of Merit $FOM$ is constructed as
$$
\mathit{FOM} = -3 \times \mathit{PAE} - \mathit{Pout}
$$

>>>>

The proposed MACE algorithm was tested using eight benchmark functions and two
real-world circuits. For the two test circuits, we used HSPICE 2012.06 to as
the simulator to get the circuit performances.

@@

We also ran the MACE algorithm in sequential mode and compared with the EI and LCB
acquisition functions. The sequential EI and LCB based Bayesian optimization
are implemented by setting the batch size $B = 1$ for EI-LP and BLCB
respectively.

The mean performances of the tested algorithms on the benchmark functions are
plotted in Figure~\ref{fig:CovPlotBenchmark}, the statistics of the final
optimization results are listed in Table~\ref{tab:result_analytical}. As can be
seen in Figure~\ref{fig:CovPlotBenchmark} and
Table~\ref{tab:result_analytical}, when running in sequential mode, the MACE
algorithm is competitive with the LCB and EI acquisition functions. The sequential MACE (MACE-1)
algorithm gave better performances than the sequential EI (EI-1) and sequential LCB (LCB-1) algorithms in the Eggholder,
Branin, Hartmann6, Ackley10, and Rosenbrock10 functions. Also, the parallel
MACE (MACE-4) gave the best performances among all the tested algorithms for
six out of the eight benchmark functions, and has shown dramatic speedup
compared to the sequential MACE (MACE-1).

@@

We want to maximize the gain, unit gain frequency (UGF) and the phase margin (PM) for this amplifier. The Figure of Merit $FOM$ is constructed as
$$
\mathit{FOM} = -1.2 \times \mathit{gain} - 10 \times \mathit{UGF} - 1.6 \times \mathit{PM}.
$$

@@

The mean convergence plot for the sequential and batch runs are given in
Figure~\ref{fig:resDAC2014}. The mean and standard deviation of the final
optimized FOM values are listed in Table~\ref{tab:result_opamp}. As can be
seen, on average, the batch MACE algorithm had the fastest convergence rate
compared with the sequential MACE algorithm and other parallel algorithms. It
should also be noted that the final optimized FOM values given by MACE-4 have
very small deviation (0.105) compared with other algorithms.

@@

For this power amplifier, we aim to maximize the power added efficiency (PAE) and the output power (Pout). The Figure of Merit $FOM$ is constructed as
$$
\mathit{FOM} = -3 \times \mathit{PAE} - \mathit{Pout}.
$$

### 2018-02-09 paper/intro.tex
minor revisions

The Bayesian optimization algorithm is a well-studied algorithm and has
demonstrated to be promising for the automated design of analog circuits.
However, the standard Bayesian optimization algorithm is sequential, it chooses
only one point at each iteration by optimizing the acquisition function. It is
often desirable to select a batch of points at each iteration, the sequential
property of Bayesian optimization limits its further applications in multi-core computer systems.

>>>>

The Bayesian optimization algorithm is a well-studied algorithm and has
demonstrated to be promising for the automated design of analog circuits.
However, the standard Bayesian optimization algorithm is sequential. It chooses
only one point at each iteration by optimizing the acquisition function. It is
often desirable to select a batch of points at each iteration. The sequential
property of Bayesian optimization limits its further applications in multi-core computer systems.

### 2018-02-09 paper/mace.tex
minor revisions

Unlike single-objective optimization, there are multiple objectives to optimize in multi-objective optimization problems\cite{MO_overview}, the multi-objective optimization problem is formulated as
\begin{equation}
    \label{eq:MOFormulation}
    \begin{aligned}
        & \text{minimize} & & f_1(\bm{x}),~\dots~,f_m(\bm{x}).
    \end{aligned}
\end{equation}
The multiple objectives to be optimizes can be conflicting, so that it is usually impossible to find a single solution that is the optimum of all objectives, the goal of multi-objective optimization algorithms is to approximate the \emph{Pareto front} of the objectives. A solution $\bm{x}_1$ is said to \emph{dominate} $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$. A design is \emph{Pareto-optimal} if it is not dominated by any other point in the design space and dominates at least one point. The whole set of the Pareto-optimal points in the design space is called the \emph{Pareto set}, and the set of Pareto-optimal points in the objective space is called the \emph{Pareto front}. It is often unlikely to get the whole Pareto front as there might be infinite points on the front, the goal of multi-objective optimization is to find a set of designs that approximates the true Pareto front.

>>>>

Unlike single-objective optimization, there are multiple objectives to optimize in multi-objective optimization problems\cite{MO_overview}. The multi-objective optimization problem is formulated as
\begin{equation}
    \label{eq:MOFormulation}
    \begin{aligned}
        & \text{minimize} & & f_1(\bm{x}),~\dots~,f_m(\bm{x}).
    \end{aligned}
\end{equation}
The multiple objectives to be optimizes can be conflicting, so that it is usually impossible to find a single solution that is the optimum of all objectives. The goal of multi-objective optimization algorithms is to approximate the \emph{Pareto front} of the objectives. A solution $\bm{x}_1$ is said to \emph{dominate} $\bm{x}_2$ if $\forall i \in \{1\dots m\},~f_i(\bm{x}_1) \le f_i(\bm{x}_2)$ and $\exists j \in \{1\dots m\}, f_j(\bm{x}_1) < f_j(\bm{x}_2)$. A design is \emph{Pareto-optimal} if it is not dominated by any other point in the design space and dominates at least one point. The whole set of the Pareto-optimal points in the design space is called the \emph{Pareto set}, and the set of Pareto-optimal points in the objective space is called the \emph{Pareto front}. It is often unlikely to get the whole Pareto front as there might be infinite points on the front. The goal of multi-objective optimization is to find a set of designs that approximates the true Pareto front.
